Toward \earlywarning\ detection of gravitational waves from compact binary coalescence

### 2011-06-30 introduction.tex
Tuned description of human validation in latency list
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1226 ccdd05d5-56c1-461a-bf98-85f6876523b4

\paragraph{Human validation (10--20~min)}%
Because the new alert system was
commissioned during S6/VSR3, humans examined each candidate for obvious flaws
before publishing an alert. This was by far the largest latency during S6/VSR3.
Hopefully, confidence in the system will grow to the point where no human intervention
is necessary before alerts are sent, so we give it no further consideration here.

>>>>

\paragraph{Human validation (10--20~min)}%
Because the new alert system was commissioned during S6/VSR3, all alerts were subjected
to quality control checks by human operators before they were disseminated.
This was by far the largest source of latency during S6/VSR3.
Hopefully, confidence in the system will grow to the point where no human intervention
is necessary before alerts are sent, so we give it no further consideration here.
